%-------------------------
% Resume in Latex
% Template from Sourabh Bajaj
% Author: Alex Rosengarten
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://alexrosengarten.com}{\Large Alexander Sky Rosengarten}} & Email : \href{mailto:alex@aira.io}{alex@aira.io}\\
  \href{http://alexrosengarten.com/}{http://www.alexrosengarten.com} & Mobile : +1-760-518-7440 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, San Diego}{La Jolla, CA}
      {B.S. Computer Science \& B.S. Cogitive Science}{Aug. 2011 -- Jun. 2016}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Aira.io}{La Jolla, CA}
      {Machine Learning/Software Engineer}{Dec 2017 - Present}
      \resumeItemListStart
	\resumeSubItem{Chloe}
	  {Developing a mobile-AI named Chloe for new product line (Android, RxJava, Java 8). }
	\resumeSubItem{Core Dialog Engine}
	  {Includes a STT/TTS system, intent matching, and conversation state management.} 
        \resumeSubItem{NSF Grant -- Real-time Object Detector}
	  {Built cloud-based AI agent using NLP, computer vision, and deep learning. AI agent can describe the color, amount, and type of 100 classes of objects in under half a second. Tool designed to assist blind/low-vision users. (Tensorflow, OpenCV, MQTT, Python 3).}
        \resumeSubItem{Wake Word Detector}
	  {Created CNN model and audio processing pipeline (Tensorflow, Android, Python 3)}
	\resumeSubItem{Bluetooth Pairing}
	  {Created a voice-only interface for connecting Android phones to bluetooth devices.}
	\resumeSubItem{Fisheye Correction}
	  {Modified Camera driver to correct video stream (C++, OpenCV).}
        \resumeSubItem{Telemetry}
	  {Built voice telemetry system, captures speech utterances from users and the device. Speech simulation added for automated testing (AWS IoT, MQTT, DynamoDB).}
      \resumeItemListEnd

    \resumeSubheading
      {Vecchio Group, UCSD Nanoengineering Department}{La Jolla, CA}
      {Research Assistant}{Jan 2018 - Present}
      \resumeItemListStart
	\resumeSubItem{Crystal Structure Classifier}
	  {Building a data pipeline and model to infer crystal structure types based on images of defraction patterns. Model has achieved 94\% accuracy accross four classes (Keras/Tensorflow).}
        \resumeSubItem{Machine Learning Instruction}
	  {Teaching graduate students programming best practices and ML concepts.}
      \resumeItemListEnd

    \resumeSubheading
      {Intuit}{San Diego, CA}
      {Software Engineer}{Aug 2016 - Nov 2017}
      \resumeItemListStart
	\resumeSubItem{ProSeries}
 	  {Developed C\# \& C++ features for Windows professional tax software.}
        \resumeSubItem{Instrumentation}
	  {Lead telemetry project, which was an outstanding need for over three years. Telemetry system is critical for new design and refactoring initiatives as well as making important business decisons. }
        \resumeSubItem{Graph Metrics}
	  {Won internal hackathon with novel idea for a telemetry system, presented to senior leadership}
        \resumeSubItem{Crash Analysis Tool Three (CATT)}
	  {Wrote app-crash analysis tool for faster, more accurate reports.}
      \resumeItemListEnd

    \resumeSubheading
      {Ingenu}{San Diego, CA}
      {Software Engineering Intern}{Mar - Aug 2016}
      \resumeItemListStart
	\resumeSubItem{SuperNova}
 	  {Developed single-page web app using Angular 1 framework}
        \resumeSubItem{Web Optimization}
	  {Reduced application load time by 44\% and kilobyte size by 40\%.}
        \resumeSubItem{RSS Widget}
	  {Prototyped, designed, and developed RSS feed aggregator (Spring, Angular)}
      \resumeItemListEnd

    \resumeSubheading
      {Natural Computation Laboratory, UCSD Dept. of Cognitive Science}{La Jolla, CA}
      {Research Assistant}{Jun 2013 - Sep 2015}
      \resumeItemListStart
	\resumeSubItem{In-Ear EEG}
 	  {Prototyped assistive wearable device to detect seizures for people with epilepsy. Created ML algortihms for detection (SVMs, OpenBCI).}
        \resumeSubItem{BCI Research}
	  {Built custom neural network layer for learned-norm pooling for EEG applications (Theano).}
        \resumeSubItem{BCI Instructor}
	  {Created hands-on workshops to teach brain-computer interface technology.}
        \resumeSubItem{BrainTag}
	  {Created a laser-tag based neurofeedback game for children with Autism (Arduino, C).}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Huh, Computer Music}
      {Open source computer music libary using functional composition and reactive streams. Presented at PyCon 2018.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\begin{tabular}{l@{\hskip 0.25in} l}
\textbf{Languages} & Python 3, Java 1.8, C++, C\#, JavaScript, Matlab, Scala/F\# \\
\textbf{Technologies} & Android, Reactive Extensions, SQL/No-SQL, AMQP, REST, AWS, Google Cloud \\
\textbf{Data Science} & Keras/Tenserflow, Scikit-Learn, OpenCV, Numpy, Pandas, Jupyter, Apache Spark \\
\textbf{Environment} & POSIX, Vim, JetBrains IDEs, Git, Docker, Vagrant, Windows
\end{tabular}

%-----------ACTIVIES & AWARDS-----------------
\section{Activities \& Awards}
Third Place Winner, {\it IEEE Brain Computer Interface Hackathon} \hfill September 2016\\
Trainee, {\it Temporal Dynamics of Learning Center} \hfill January 2014 - June 2015 \\  
Founding Member, {\it Data Science Student Society} \hfill November 2014 - September 2015 \\
Computer Science Tutor, {\it UCSD CSE Department} \hfill Spring 2013, Summer 2014 \\
Summer Research Scholar, {\it Qualcomm Institute/Calit2} \hfill June - August 2013 \\   
President, {\it Cognitive Science Student Association} \hfill August 2012 - January 2014 \\



%-------------------------------------------
\end{document}

