% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 


%\setlength{\textwidth}{5.1in} % set width of text portion
%\addtolength{\topmargin}{-.65in} % Set margin top 
%\addtolength{\textheight}{1.75in} % Set margin bottom
\usepackage[letterpaper, tmargin=.10in, bmargin=.10in, lmargin = .25in, rmargin=1.75in, marginparwidth=0in]{geometry}



\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Alexander S. Rosengarten}
% Draw a horizontal line the whole width of resume:

 \moveleft\hoffset\vbox{\hrule width 7.5in height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{PO Box 231048, Encinitas CA 92024    |  alexrosengarten@gmail.com | github.com/alxrsngrtn}

  \section{EDUCATION} University of California, San Diego, La Jolla, CA \hfill   June 2016 \\
		  {\sl B.S.} Computer Science  (Major GPA: 3.63) \& {\sl B.S.} Cognitive Science (Major GPA: 3.64).

\section{SOFT \\ SKILLS}
Strong analytical \& problem solving ability, Team player, Humble, Quick-learner, Self-motivated, Innovative


\section{TECHNICAL \\ SKILLS} 
	
%\begin{tabular}{l l l}
% 								Experience & Languages & Technologies \\ \hline
%								Adept	&   \parbox[t]{2.4in}{Python, Java, Javascript, C/C++,  Matlab/Julia}   & %\parbox[t]{2.4in}{Numpy/Pandas, Angular.js, Webpack, Git, Theano, Jet Brains IDEs} \\
%								Proficient &  \parbox[t]{2.4in}{C\#, Scala} & \parbox[t]{2.4in}{Docker, Express.js, Ionic/%Cordova, SQL, Apache Spark, Spring MVC, }\\ % Hadoop
%								% Adobe Creative Suite, Android Studio, Arduino, Eclipse, GDB, Git, Unix, Vim
%\end{tabular}
\begin{tabular}{l l}
Languages & Python, C\#, C++, JavaScript, Java, Matlab/Octave/Julia, F\#, Scala  \\
Frontend & Angular.js, Jasmine, Ionic/Cordova, Grunt/Gulp, Webpack \\
Backend & SQL, Cassandra, Flask, Node.js, Django, Neo4j, Spring boot \\
Data & Keras/Tenserflow/Theano, Scikit-Learn, Apache Spark \\
Environment & Git, Docker, Vagrant, Unix/Windows, SVM, Perforce
\end{tabular}


% Talk about the challenge that had to be done, the  actions that you took to tackle the challenge, and the results (how things outside of yourself were experienced)		
\section{WORK EXPERIENCE} 
		{\sl Software Engineer} \hfill            August 2016 - Present \\
                Intuit, San Diego, CA
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Developing C\# and C++ features for ProSeries, Windows professional tax software. 
                 \item Won business unit hackathon with original idea, presented to senior leadership.
                 \item Leading telemetry project on team, filling an outstanding need of over three years.  
                 \item Wrote Python tool to analyze application crash logs more precisely in half the time.
                 \item Managing software-focused book club, leading to process changes and superior technical ability of team.
                 \end{itemize} 


		{\sl Software Engineering Intern} \hfill            March - August 2016 \\
                Ingenu, San Diego, CA
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Developed single-page web application with Angular 1 framework.
                 \item Prototyped, designed, and developed RSS feed sanitizer and aggregator (Spring boot, Angular).
                 \item Rearchitected unit test system (Karma). Wrote unit and integration tests (Jasmine, Protractor/Selenium).
                 \item Reduced application load time by 44\% and KB size by 40\% via minification, lazy loading, and CDN.
                 \end{itemize} 
	
		{\sl Principal Frontend Engineer} \hfill            December 2015 - June 2016 \\
                Guardiome, La Jolla, CA
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Developed GUI for a genome exploration tool from scratch (Python). 
                 \item Integrated with bioinformatics software on a secure, embedded hardware system (Debian).
                 \end{itemize} 

		{\sl Research Assistant} \hfill            June 2013 - September 2015 \\
                Natural Computation Laboratory, UCSD Dept. of Cognitive Science, La Jolla, CA
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Developed BrainTag: open source neurofeedback game for children with Autism (Arduino, C). 
                 \item Created hands-on workshops to teach brain computer interface technology (OpenBCI, Python).
                 %\item Wrote data visualization and machine learning toolbox for open source brain-computer interface system (Python, Java, C, Javascript). 
                 \end{itemize} 
	
		%{\sl Computer Science Tutor} \hfill 	April - June 2013, August 2014 \\
		%UCSD Computer Science Department, La Jolla, CA
                 %\begin{itemize}  \itemsep -2pt % reduce space between 
                 %\item Spring 2013, Matlab Programming: Tutored students, debugged code, graded exams and assignments.
                 %\item Summer 2014, Systems Programing: Tutored students in C and ARM Assembly programming course, implemented on Raspberry Pi. Found errors and debugged code (ARM, C, Raspberry Pi). 
                 %\end{itemize}
                 
                %{\sl Research Programmer} \hfill            July - December 2012 \\
                %Radiology Laboratory, UCSD School of Medicine, Sorrento Valley, CA
                 %\begin{itemize}  \itemsep -2pt %reduce space between items
                 %\item Performed computer aided statistical analysis and data visualization of MRI data (Matlab, FreeSurer).
                 %\item Collected EEG and MEG data.
                 %\end{itemize} 
                


    
\section{PROJECTS}
                 % include quantitative results
                {\sl Forward 135 - Full Stack Developer} \hfill 	 April - June 2016 \\
                Server-Side Web Applications Course, La Jolla, CA 
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Built a full-stack architecture for efficient change propagation from the server to the client, part of a research/class project. Worked in a team of three.
                 \item Project only sends the changes in a database to each client via WebSockets (Javascript ES6, Webpack, Socket.io). 
                 \item Performed Incremental View Maintenance via materialized views and database triggers (PostgreSQL). 
                 \end{itemize}
                 
		 {\sl In-Ear EEG - Software Team Member} \hfill 	 April - June 2015 \\
                Embedded Systems Project Course, La Jolla, CA 
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Worked in team to create In-Ear EEG device for people with epilepsy.
                 \item Wrote machine learning code with a partner to detect presence of epileptic seizures (Matlab, OpenBCI).
                 \item Built server that stored 20 minutes of brainwave data once seizures are detected (Python, SQLite). 
                 \end{itemize}
                
\section{COURSEWORK}
   
   \begin{tabular}{l l l}
   $\bullet$ Advanced Data Structures  & $\bullet$ Advanced Machine Learning & $\bullet$ Algorithms \\
   $\bullet$ Compiler Construction & $\bullet$ Computer Vision & $\bullet$ Neural Networks \\ 
   $\bullet$ Operating Systems  &  $\bullet$ Programming Languages & $\bullet$ Server-Side Web Applications  \\
     
    \end{tabular}
     %\footnotetext[1]{Left early for medical reasons}
    %\footnotetext[1]{Currently Enrolled}
  
                 
\section{ AWARDS \& ACTIVITIES }  
	    Third Place Winner, {\it IEEE Brain Computer Interface Hackathon} \hfill September 2016\\  
   	    Founding Member, {\it Data Science Student Society} \hfill November 2014 - September 2015 \\
	    Summer Research Scholar, {\it Qualcomm Institute/Calit2} \hfill June - August 2013 \\         
            President, {\it Cognitive Science Student Association} \hfill August 2012 - January 2014 \\
            
%\end{resume}
\end{document}







